Preliminary Thesis Defence

### 2013-11-13 draft.tex
fix title
first draft
test combine
draft combine try
new structure using subfiles

\documentclass[a4paper,12pt]{report}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\usepackage{alltt}
\usepackage{hyperref}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\title{Preliminary Thesis Defence\\~\\ Supervisor: Jean-Louis Arcand\\ Second Reader: Love Vanderwalle}
\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva. bquast@gmail.com}}
\maketitle

@@

\chapter{Surviving Andersonville}
Survival analysis

@@

\chapter{Police Reform Conkary}
Guinea bla bla.

\chapter{Bitcoin remitances}
How I...

@@

\chapter{Singh}
The difference between risk and uncertainty.

>>>>

\documentclass[a4paper]{report}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\usepackage{alltt}
\usepackage{subfiles}
\usepackage{hyperref}

\title{Preliminary Thesis Defence}
%\subtitle{
%\begin{tabular}{rl}
%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
%\end{tabular}
%}

\author{Bastiaan Quast\thanks{PhD Student, The Graduate Institute, Geneva; bastiaan.quast@graduateinstitute.ch / bquast@gmail.com}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\maketitle

@@

\chapter{Surviving Andersonville}
article

@@

\chapter{Police Reform Conkary}
\subfile{conakry.tex}

\chapter{Bitcoin remitances}
\subfile{bitcoin.tex}

@@

\chapter{Morris Shin 1998, Unique equilibrium in a model of self-fulfilling currency attacks}
\subfile{MorrisShin.tex}

\chapter*{End notes}
